Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-14 analysis/sim/run_simpw.Rmd
fig3 legend

legend("bottomleft", inset=.02, title="tool",
   c("CP default","CP BG fix","CP FDR fix","CP BG and FDR fix","fora","fgsea"),
   col=c("black","orange","darkgreen","purple","red","blue"),horiz=FALSE, cex=1.2, pch=19,lwd=2)

@@

plot(cp$VARIANCE,cp$p,ylim=c(0,1),type="b",pch=19,xlab="variance added",ylab="index",main="precision")
points(cpbg$VARIANCE,cpbg$p,type="b",pch=19,col="orange")
points(cpfdr$VARIANCE,cpfdr$p,type="b",pch=19,col="darkgreen")
points(cpbgfdr$VARIANCE,cpbgfdr$p,type="b",pch=19,col="purple")
points(fo$VARIANCE,fo$p,type="b",pch=19,col="red")
points(fg$VARIANCE,fg$p,type="b",pch=19,col="blue")
grid()
legend("bottomleft", inset=.02, title="tool",
   c("CP default","CP BG fix","CP FDR fix","CP BG and FDR fix","fora","fgsea"),
   col=c("black","orange","darkgreen","purple","red","blue"),
   horiz=FALSE, cex=1.2, pch=19,lwd=2)

>>>>

legend("bottomleft", inset=.02, title="tool",
   c("CP default","CP BG fix","CP FDR fix","CP BG and FDR fix","fora","fgsea"),
   col=c("black","orange","darkgreen","purple","red","blue"),horiz=FALSE, cex=1.0, pch=19,lwd=2)

@@

plot(cp$VARIANCE,cp$p,ylim=c(0,1),type="b",pch=19,xlab="variance added",ylab="index",main="precision")
points(cpbg$VARIANCE,cpbg$p,type="b",pch=19,col="orange")
points(cpfdr$VARIANCE,cpfdr$p,type="b",pch=19,col="darkgreen")
points(cpbgfdr$VARIANCE,cpbgfdr$p,type="b",pch=19,col="purple")
points(fo$VARIANCE,fo$p,type="b",pch=19,col="red")
points(fg$VARIANCE,fg$p,type="b",pch=19,col="blue")
grid()
legend("bottomleft", inset=.02, title="tool",
   c("CP default","CP BG fix","CP FDR fix","CP BG and FDR fix","fora","fgsea"),
   col=c("black","orange","darkgreen","purple","red","blue"),
   horiz=FALSE, cex=1.0, pch=19,lwd=2)
